Graph bipartitioning and you

### 2016-01-14 evolutionaryComputation/2-practical/report.tex
using the original data

I implemented GLS with the evolution class. The only thing I had to do really
was write the crossover method, the rest was already functional.
\section{TODO}
MLS with several results
\end{document}

>>>>

I implemented GLS with the evolution class. The only thing I had to do really
was write the crossover method, the rest was already functional.

I wanted to see if the GLS popsize and selection pressure would have any
effect on the average fitness found. I suspect that a bigger population size
would find better results and that weaker selection would find better
average scores.

I chose to investigate with population sizes of 25, 50 and 75. I didn't want
to wait to long on this and the runtime for 50 was approaching ~10 minutes
for the slowest. Luckily I have a powerfull laptop and can use paralization.

Doing this 30 times to cancel the staostic effect would result into ~5 hours.
\section{TODO}
MLS with several results
GLS -> I think the localsearch will recursively unecesrly decend into its members
because the local search is packed in the member factory. Maybe remove the
local search from the memberfactory?

Use original file by doing a substr(30)
\end{document}
